Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-09-08 ms/manuscript.Rmd
Fix missing label in y-axis of Fig 4
- adds check for missing labels

indep_var_lookup <-
  tibble(
    term = c("area", "I(temp^2)", "null_model", "percent_apo", "precip", "precip_season", "temp"),
    term_print = c("Area", "Temp^2", "Null model", "% apomictic", "Precip.", "Precip.\nseasonality", "Temp.")
  ) %>%
  # Include "plain" version of term for arranging alphabetically
  mutate(term_plain = str_replace_all(term, fixed("I(temp^2)"), "temp^2"))

@@

# Format parameter values for plotting
model_params_for_plot <-
  model_params %>%
  # add model type
  tidyr::extract(formula, "model_type", regex = " ~ ([^ ]+) ") %>%
  # drop intercept
  filter(term != "(Intercept)") %>%
  # add LRT results and names formatted for printing
  left_join(lrt_signif, by = c("resp_var", "term", "model_type")) %>%
  left_join(resp_var_lookup, by = "resp_var") %>%
  left_join(indep_var_lookup, by = "term") %>%
  left_join(model_type_lookup, by = "model_type") %>%
  # Make coefficient with greatest abs t-value bold
  group_by(resp_var, model_type) %>%
  mutate(
    term_print = case_when(
      abs(t_value) == max(abs(t_value)) ~ glue::glue("**{term_print}**"),
      TRUE ~ term_print
    ),
    term_print = factor(term_print)
  ) %>%
  ungroup()

>>>>

indep_var_lookup <-
  tibble(
    term = c("lat_area", "I(temp^2)", "null_model", "percent_apo", "precip", "precip_season", "temp"),
    term_print = c("Area", "Temp^2", "Null model", "% apomictic", "Precip.", "Precip.\nseasonality", "Temp.")
  ) %>%
  # Include "plain" version of term for arranging alphabetically
  mutate(term_plain = str_replace_all(term, fixed("I(temp^2)"), "temp^2"))

@@

# Format parameter values for plotting
model_params_for_plot <-
  model_params %>%
  # add model type
  tidyr::extract(formula, "model_type", regex = " ~ ([^ ]+) ") %>%
  # drop intercept
  filter(term != "(Intercept)") %>%
  # add LRT results and names formatted for printing
  left_join(lrt_signif, by = c("resp_var", "term", "model_type")) %>%
  left_join(resp_var_lookup, by = "resp_var") %>%
  left_join(indep_var_lookup, by = "term") %>%
  left_join(model_type_lookup, by = "model_type") %>%
  # Make coefficient with greatest abs t-value bold
  group_by(resp_var, model_type) %>%
  mutate(
    term_print = case_when(
      abs(t_value) == max(abs(t_value)) ~ glue::glue("**{term_print}**"),
      TRUE ~ term_print
    ),
    term_print = factor(term_print)
  ) %>%
  ungroup() %>%
  assert(not_na, matches("print|plain"))
